
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing


\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\newcommand{\negpar}[1][-7em]{%
  \ifvmode\else\par\fi
  {\parindent=#1\leavevmode}\ignorespaces
}
\newcommand{\negparr}[1][-17em]{%
  \ifvmode\else\par\fi
  {\parindent=#1\leavevmode}\ignorespaces
}
\usepackage{color}
\begin{document}

\header{Jai Krishna Srikanth }{Kolliboyana}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
1240 w Farwell Avenue, 1A
Chicago,IL- 60626
~
+1 (989) 423-4811
~
\href{mailto:jaikolliboyana@gmail.com}{jaikolliboyana@gmail.com}
\section{languages}
Telugu ({\emph mother tongue})
English \& Hindi ({\emph Fluent})
\section{Professional Memberships}
Andhra Pradesh State Dental Council, Indian Dental Association
\section{Memberships}
CMU Voting Booth, Mary Ellen Brandell Volunteer Center, Office of Student Activities \& Involvement
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2014 -- 2015}
{Masters of Science in Administration}
{\bf Central Michigan University MI USA}
{{\bf Major:} \emph{Health Services Administration}\\ {\bf GPA:} \emph{3.62}}
%------------------------------------------------
\entry
{2002 -- 2007}
%{Bachelors {\normalfont of Dental Surgery}}
{Bachelors of Dental Surgery}
{\bf Dr. NTR University of Health Sciences AP India}
{{\bf Major:} \emph{Dentistry \& Public Health Dentistry} \\ {\bf Minor:} \emph{Basic Human Sciences, Biostatictics} \\ {\bf GPA:} \emph{3.87}}
%------------------------------------------------
\entry
{1999 -- 2000}
{Board of Intermediate Education}
{\bf Sri Chaitanya Junior College AP India}
{{\bf Major:} \emph{Biology} \\ {\bf Minor:} \emph{Physics and Organic Chemistry}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{Feb 2010 - Oct 2013}
{Community Health Centre}
{\bf Bobbili A.P India}
{
\begin{itemize}
	\item \emph{Role:} Consulting Dentist
	\item \emph{Division:} Dentistry \& Dental Surgery
\end{itemize}
}
%------------------------------------------------
\entry
{Aug 2008 -- Jan 2010}
{Dr. Sudha \& Nageswara Rao Institute of Dental Sciences}
{\bf Vijayawada A.P India}
{
\begin{itemize}
	\item \emph{Role:} Junior Lecturer\\
\end{itemize}
}
%------------------------------------------------
\entry
{Jul 2007 -- Jun 2008}
{St. Joseph Dental College and Hospital}
{\bf Eluru AP India}
{
\begin{itemize}
	\item Rotatory Internship Certification in Dentistry
\end{itemize}
}

%------------------------------------------------
\end{entrylist}

\section{Publication}
\begin{entrylist}
%------------------------------------------------
\entry
{Sep 2014}
{Endodontic Management of Radix Entomolaris in Mandibular First Molars -- Two Case Reports}
{}
{
	\emph{\bf Authors: } Ravi Kanth Chintala, Mahesh Gowda, Potharaju Santhi Priya and Jai Krishna Srikanth Kolliboyana\\
	\emph{\bf Journal:} International journal of Scientific Research\\
	\emph{\bf Vol:} 3\\
	\emph{\bf Issue:} 9\\
	\emph{\bf ISSN No: } 2277 -8179\\
	\emph{\bf Page: } 355 -- 357\\
}
%------------------------------------------------
\end{entrylist}
\newpage
\section{Professional \& Volunteering Experience}
\begin{entrylist}
%------------------------------------------------

\entry
{Dec 2015 -- \\Present}
{\large Research Assistant}
{\bf University of Illinois at Chicago -- College of Dentistry, IL}
{
	{\bf Topic: }Actively involved in learning and assisting in ongoing research of understanding the role of DNA damage protein in the progression of oral/head and neck cancer. I am responsible for culturing oral cancer cells and looking at various proteins involved in DNA damage signaling pathway. This research has significant impact on studying progression of DNA damage induced oncogenesis. \\
	{\bf Under: } Mr. Prashant Bommi PhD and Dr. Srilatha Bagchi PhD \\
}

\entry
{Nov 2014 -- Nov 2015}
{\large Externship}
{\bf Mount Pleasant MI USA}
{
	\emph{\bf Under: } Dr. Kenneth Egger, DDS\\
	\emph{\bf Clinic: } Family Dentistry\\
	\emph{\bf URL: }www.mountpleasantmidentist.com
}
\\
\entry
{2010 -- 2011}
{\large Research Assistant}
{\bf Government Dental College AP India}
{
	{\bf Topic: } Treatment of human gingival recession by coronally positioned flap procedure with or without GTR- a clinical study.\\
	{\bf Under: } Dr. Santha Kumari Pothuraju, MDS (Department Chairperson)\\
}

\entry
{2016}
{\large Volunteering in free dental education programs}
{\bf UIC - College of Dentistry, IL USA}
{
	{\bf Under:} Division of Prevention and Public Health Sciences.
}
\\
\entry
{2014 -- 2015}
{\large Mary Ellen Brandell Volunteer Center}
{\bf Central Michigan University MI USA}
{
	{\bf Involvement History}
	\begin{enumerate}
		\item Alternate Spring break - Child Homes, Lansing
		\item Service Ambassadors - Isabella County
		\item Earth Week
		\item Service Ambassadors - Ronald McDonald House
	\end{enumerate}
}
\\
\entry
{2010 - 2013}
{\large Volunteer as Dentist at Community Health Centre}
{\bf Bobbili AP India}
{
	{\bf Involvement History}
	\begin{enumerate}
		\item Actively Participated in Anti-Tobacco campaigns and educated people about ill effects of tobacco through periodical monitoring of formation of pre-cancerous lesions and helped people to abandon tobacco usage by regular counseling and follow-up.
		\item Training in Dental treatment and rehabilitation procedures on patients.
	\end{enumerate}
}
\\
\entry
{2007 - 2009}
{\large Volunteer as Dentist during Residency and Junior Lectureship}
{\bf AP India}
{
	{\bf Involvement History}
	\begin{enumerate}
		\item Attended 46 camps on health promotion and disease prevention in many rural areas during 2007-2009 (Examples: Role of HPV in oral carcinoma, treatment and awareness of fluorosis) which were attended by 600 women, men and children.
	\end{enumerate}
}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	CERTIFICATION SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Computer Skills\cite{paper}}
{\bf Platforms: } Windows XP, Windows 7, OS X
{\bf Office Products: }MS Word, Excel, PowerPoint
{\bf Other: }Prezi
\end{aside}
%------------------------------------------------
%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\newpage
\section{Honors \& Awards}
\begin{entrylist}
%------------------------------------------------
\entry
{Feb 2014}
{Out-of-State Tuition Merit Award}
{Central Michigan University MI USA}
{}
\entry
{Feb 2013}
{Doctor worth Appreciation}
{Bobbili Panchayat Board AP India}
{}
\entry
{Nov 2007}
{{\bf Second Prize } in Indo-Italiam Dental Congress}
{St Joseph Dental College AP India}
{Sinus Augmentation}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	CERTIFICATION SECTION
%----------------------------------------------------------------------------------------

\section{Certifications}
\begin{entrylist}
%------------------------------------------------
\entry
{Sep 2014}
{Social \& Behavioral Research -- Based/Refresher Curriculum Completion Report}
{}
{Collaborative Institutional Training Initiative (CITI)}
%------------------------------------------------
\entry
{Nov 2014}
{Six Sigma White Belt Certificate of Achievement}
{}
{}
%------------------------------------------------
\entry
{Oct 2010}
{Advanced Tally Financial Accounting  Program (Tally.ERP9)}
{Damodram Computer Education Center}
{}
%------------------------------------------------
\entry
{2007 -- 2008}
{Rotatory internship Certification in Dentistry}
{St. Joseph Dental College, Eluru, A.P, India}
{}
%------------------------------------------------
\entry
{May 2009}
{Basics of Clinical Research}
{Certificate of Participation}
{}
%-------------------------------------------------
\entry
{April 2015}
{International Children's Book-Read In!}
{Certificate of Appreciation}
{Central Michigan University}
\end{entrylist}
%------------------------------------------------


\section{Conferences \& Seminars}
\negpar
%{\small Attended}
\negpar
\begin{tabular}{|c |c |c |c|}
\hline
  {\bf Type of activity}	&	{\bf Particular topic / presenter}		&	{\bf Date}	&	{\bf Venue} \\
\hline
\hline
Conference	&	26\textsuperscript{th} A.P State Dental Conference	&	23\textsuperscript{rd} \& 24\textsuperscript{th} December 2005		&	Hyderabad, AP\\
\hline
Conference	&	First Indo-Italian Dental Congress				&	3\textsuperscript{rd} -- 4\textsuperscript{th} November 2007		&	Eluru, AP\\
\hline
Seminar		&	{Research Methodology by Dr K Ranganadhan}	&	18\textsuperscript{th} \& 19\textsuperscript{th} Oct 2008		&	Guntur, AP\\
\hline
Conference	&	29\textsuperscript{th} AP State Dental Conference	& 5\textsuperscript{th}, 6\textsuperscript{th} \& 7\textsuperscript{th} Dec 2008	&	Warangal AP\\
\hline
Conference	&	XXIV FODI and XVII IES National Conference		&	13\textsuperscript{th} to 15\textsuperscript{th} Nov 2009	& Cochin Kerala\\
\hline
Conference	& Perioview 2010 \& 3\textsuperscript{rd} ASP Convention	&	21\textsuperscript{st} \& 22\textsuperscript{nd} Aug 2010 	&	Vizag AP\\
\hline
Conference	& XXVI FODI and XIX IES National Conference			& 11\textsuperscript{th} to 13\textsuperscript{th} Nov 2011		&	New Delhi\\
\hline
\end{tabular}


%----------------------------------------------------------------------------------------
\section{Posters \& Papers}
\negparr
%{\small Presented}
\negparr
\begin{tabular}{|c |c |c |c|}
\hline
  {\bf Type of Presentation/Poster/Paper}	&	{\bf Particular topic / presenter}		&	{\bf Date}	&	{\bf Venue} \\
\hline
Poster		& 	{\bf Sinus Augmentation}		&	3\textsuperscript{rd} - 4\textsuperscript{th} Nov 2007		&	{First Indo-Italian Dental Congress} Eluru AP\\
\hline
Paper		& {\bf Endo-Perio-A Diagnostic Dilemma??}	&	Aug\textsuperscript{th} 2009	&	\emph{ Properend -} Mamta Dental College Khammam AP\\
\hline
Poster		& {\bf Ultrasonics in Endodontics}		& Nov 2009	& XXVI FODI and XVII IES National Conference Kerala\\
\hline
\end{tabular}

\newpage
\section{Workshop \& Continuing Dental Educational Programs}
\negparr
%{\small Attended}

\negparr
\begin{tabular}{|c |c |c |c|}
\hline
    {\bf Type of Activities}	&	{\bf Particular topic / presenter}		&	{\bf Date}	&	 {\bf Venue}\\
\hline
    {\bf CDE Program}	&	{\bf One Visit Reciprocating Endodontics}		&	{ 14\textsuperscript{th} Jan 2015}	&	{University of Michigan Ann Arbor} \\
\hline
Workshop		&	{\bf Dental Photography} by Dr. Akhtar Hussain	&	24\textsuperscript{th} Oct 2008		&	Gitam Dental College Vizag AP\\
\hline
Workshop		&	{\bf Magnificent Microscopes}	&	7\textsuperscript{th} Mar 2009	&	Vishnu Dental College Bhimavaram AP\\
\hline
CDE	Program	& 	{\bf Rotary Endodontics - Endodontics} by Dr. Gary R Hartwell	& 28\textsuperscript{th} July 2009	&	Guntur AP\\
\hline
CDE Program	&	{\bf Dr NTRUHS Zonal CDE Program}	& 22\textsuperscript{th} Dec 2011	&	SIDS Chinnautpalli AP\\
\hline
Workshop		&	{\bf "Hands on single file endodontic"} Dr Julian Webber	& 18\textsuperscript{th} June 2012	&	New Delhi\\
\hline
CDE Program	&	{\bf Clinical innovations India}	&	6\textsuperscript{th} \& 7\textsuperscript{th} April 2013	&	New Delhi\\
\hline
\end{tabular}

%----------------------------------------------------------------------------------------
%	Skills & Experience
%---------------------------------------------------------------------------------------
\section{Strengths:}
Good understanding of preventive methods and Epidemiological concepts.\\
A profound understanding about the etiology and pathogenesis of common diseases.\\
Perseverance in handling assiduous tasks with good analytical skills.\\
Familiarizing with new and latest technology advancements in dentistry.

\section{Extra Curricular Activities \& Hobbies }
Painting, Reading, Swimming, Traveling, Photography.\\
Represented my college in Inter-Dental College Sports Event.

\end{document}




